SHARP IV: Flux ratio anomalies from disks in the Illustris simulation

### 2016-08-09 papers/illustris_disk/ms.tex
update disk paper draft

\section{Introduction}
\section{The Illustris simulation}
\section{Disks selection}
\begin{itemize}
\item discuss how realistic disks in illustris are
\end{itemize}
\subsection{Morphological selection}
\subsection{Kinematical selection I}
\subsection{Kinematical selection II}
\section{Disk properties}
\begin{itemize}
\item how many galaxies have disks
\item mass in disk
\item redshift evolution
\item comparison with B1555 and SWELLS
\item observability of the disks
\end{itemize}
\section{Flux ratio anomalies from disks}

>>>>

\section{Introduction}
\section{The Illustris simulation}
\section{Disks selection}
\begin{itemize}
\item discuss how realistic disks in illustris are
\end{itemize}
Resolution: stellar mass cut between 7E9Msun~1E10Msun. Due to the resolution limitation, our disk galaxy samples are from the high-mass range of disk galaxy population, with mass range [].

\subsection{Morphological selection}
Photometric properties are commonly used in surveys to identify the morphology type of galaxies. Star particles in simulation can also be visualized (SUNRISE) and provide photometric observants for individual galaxy. We apply the following two criteria to identity a disk galaxy in Illustris simulation: 1) The galaxy has a 
better fit (i.e. a smaller $\chi^2$) in exponential disk light profile than in de Vaucouleur light profile, and 2) the galaxy has a Sersic index smaller than two. The sample selected by these photometric properties are called morphological selection in this work.

\subsection{Kinematical selection I}
In kinematical view, stellar disk is a group of stars co-rotate in the same direction with the common symmetric axis. One of the advantages in simulations is that one can access to the full detail of kinematical properties for single mass particle. These kinematical properties provide an approach to decompose different components in disk galaxy: thin disk, thick disk, and spheroid.
z-component angular momentum (symmetric axis)
Jz vs binding energy: $J_{circ}$ curve
circularity parameter $\epsilon_z = Jz/J_{circ}$

decomposition: thin disk+thick disk+spheroid

thin disk star fraction larger than 40\%

\subsection{Kinematical selection II}
stars in spheroid: bulge stars
bulge star fraction less than 60\%
\section{Disk properties}
\begin{itemize}
\item how many galaxies have disks
\item mass in disk
\item redshift evolution
\item comparison with B1555 and SWELLS
\item observability of the disks
\end{itemize}
\section{Flux ratio anomalies from disks}
